---
title: 'The Identification of Bacteria on Individual versus Communal PC Keyboards'
author: "Jacinda Chen"
date: "October 6, 2019"
output: word_document
csl: bioinformatics.csl
bibliography: references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Computers have become an essential part of college life as a result of the increased need of the internet. Food and drinks are constantly consumed around keyboards, which might provide food for whatever is living on top of the keyboard, if there is [@malik2014study]. Therefore, more and more students are required to buy or have access to computers. Keyboards are being touched constantly in personal laptops as well as shared computers that the university offers and most people are not aware of the number of microorganisms present on their keyboards [@al2011bacterial]. I will be comparing the bacteria found on the keyboards of individual students' laptops versus the keyboards of shared computers on the USF campus. Previous research done on this topic has found that shared computers had more microorganisms than individual computers [@anderson2009microbial]. This project will circle around hygiene and aim to figure out if shared computers should be cleaned more often or if personal laptops are not as sanitary as they seem.  

# Methods

## Study design

### Bacterial Collection

The surface samples were collected during the lab section of the Bioinformatics class on September 3rd, 2019. In total, twelve tubes were collected (two tubes per sample in four different locations). For each location, two different keys on the keyboard was swabbed. Each sterile swab was dipped in sterile PBS (Phosphate Buffer Saline at pH 7.4)to moisten, then wrung of excess PBS against the side of the tube. The surface was then swabbed for 15 seconds. The tip of the swab was broken off into a labelled eppendorf with initials, date,and an unique sample ID. Samples were gathered first in the first floor of Toler Hall, where one sample was gathered for the "A" key and another two samples were gathered for the "F" key on the shared computer at the front desk and put into labelled eppendorfs called "1A" and "1F" respectively. On the fourth floor of the University Center, specifically in the graphics center on a shared computer, samples were gathered and put into labelled eppendorfs called "2A" and "2F". On the first floor of the library, where samples were gathered on a shared computer, samples were once again gathered and put into labelled eppendorfs called "3A" and "3F". Inside the Bioinformatics class, samples were gathered from three different laptops from three different students. Student A's samples were gathered and inserted into labelled eppendorfs "4A" and "4F", Student B's samples were gathered and inserted into labelled eppendorfs "5A" and "5F", and Student C's samples were gathered and inserted into labelled eppendorfs "6A" and "6F". The "A" key samples were put directly into the freezer at -20^o Celcius.

### Dilution Series

The dilution series was done with the "F" key group. In order to prepare the undiluted group, I put 200 microliters of PBS into the six eppendorfs with swabs. These six eppendorfs were then vortexed for fifteen seconds. There were another six eppendorfs that were dedicated to 1:10 dilutions of the original six eppendorfs. For these six 1:10 dilution eppendorfs, I added 180 microliters of PBS to each of them. Twenty microliters of the one undiluted eppendorf was then added to its respective 1:10 dilution eppendorf to complete the dilution. This was then repeated another five times to complete the other 1:10 dilutions. I vortexed these six eppendorfs for five seconds. In order to do the 1:100 dilutions, I once again added 180 microliters of PBS into each of the six eppendorfs labelled respectively to the undiluted and the 1:10 dilution series. Twenty microliters of a 1:10 dilution was then added to its respectively labelled 1:100 dilution eppendorf. I repeated this step for the other five 1:100 dilution eppendorfs. The six 1:100 dilution eppendorfs were then vortexed for 5 seconds.

### Plating "F" Key Group

I used 18 100 mm TSA(Tryptic soy agar) plates for plating samples from each of my 2 treatments (n = 3 per group, 6 total). I put 100 microliters of an eppendorf from the undiluted series onto a TSA plate and used sterile rattler Plating Beads (5 mm) to spread the medium evenly across the TSA plate. I repeated this step for the other five eppendorfs from the undiluted series, the six eppendorfs from the 1:10 dilution series, as well as six eppendorfs from the 1:100 dilution series. These 18 TSA plates were then incubated at 37^o Celcius for a week.

### DNA Extraction



## Analysis

Bacterial Collection: For each location, two different keys on the keyboard was swabbed because there was not enough surface area on one key to be swabbed twice. 

Dilution Series: I split the samples into two groups: key "A" and key "F". The "A" key group was put directly into the freezer at -20^o Celcius so data could be extracted directly from those samples at a later date (only looking at dead bacteria). The dilution series was done with the "F" key group. Since it was not known what type of bacteria it was nor how much of it would grow, it was necessary to dilute the samples in order to maximize the number of environments that the bacteria could possibly grow in. The undiluted series were vortexed for 15 seconds in order to get the bacteria off the swabs and into the PBS. *Talk about why vortex* 

# Results

## Culture Data

```{r culture-abundances-1x}
# Make a boxplot of undiluted culture abundances
culture_data <- read.csv("data")
```

# Discussion

# Sources Cited
